\documentclass[11pt, titlepage, a4paper]{article}

\usepackage{graphicx} % For images
\usepackage{lipsum} % For sample text
\usepackage[utf8]{inputenc} % For special characters
\usepackage[english]{babel} % For language-specific hyphenation patterns
\usepackage[hidelinks]{hyperref} % For clickable links
\usepackage{enumitem}
\usepackage[]{datetime2}
\usepackage[a4paper, total={15.0cm, 25cm}]{geometry}
\def\labelitemi{--}

\title{Learning Agreement}
\author{Emily Sterthaus \\ Matriculation Number: 451 342 \\ \href{mailto:m_ster15@uni-muenster.de}{m\_ster15@uni-muenster.de}}
\date{\today}

\begin{document}

\maketitle
\newpage

\section{Internship Details}
In the following section basic information's about the internship will be provided.

\begin{description}[]
    \item[Intern:] Emily Sterthaus
    \item[College/University:] Westf채lische Wilhelms-Universit채t M체nster
    \item[Degree Program:] Master of Science Geoinformatics and Spatial Data Science
    \item[Internship Provider:] con terra GmbH
    \item[Internship Location] Martin-Luther-King-Weg 20, 48155 M체nster, Germany
    \item[Department:] Open Data and Copernicus
    \item[Internship Supervisor:] Thore Fechner, \href{mailto:t.fechner@conterra.de}{t.fechner@conterra.de}
    \item[Supervisor Frequency:] Bi-weekly
    \item[Internship Duration:]  196 consecutive days $\approx$ 6.5 Months
    \item[Expected Hours per Day:] 6,4 Hours
    \item[Expected Hours per Week:] 32 Hours 
    \item[Start Date:] 2023-09-01
    \item[Remote Work:] Mixed, at least 50\% on site
    \end{description}
    
The Internship will be done for 25 ECTS. Therefore the total work time will be 750 Hours. The planned duration already accounts for Vacation and Holidays.
In case the student does not meet the required Work Hours, the internship will be extended until the needed hours are reached. The hours per day/week are just an estimation and can vary. 


\section{Learning Objectives}
The primarily goal of the internship is to gain practical experience in the field of software development. The following list contains the learning objectives for the internship. 
\begin{itemize}
    \item \textbf{Technical Skills}
    \begin{itemize}
        \item Enhancement of proficiency in GIS software and infrastructure
        \item Further development of coding and data analysis capabilities
        \item Mastery in data management
        \item Acquisition of knowledge in emerging technology standards
    \end{itemize}
    \item \textbf{Soft Skills}
    \begin{itemize}
        \item Familiarization with project management and participation in large-scale projects
        \item Development of collaborative skills for team environments
        \item Improvement in effective communication strategies
    \end{itemize}
    \item \textbf{Conceptual Skills}
    \begin{itemize}
        \item Skill development in recognizing correlations between various topics
        \item Improvement in strategizing for problem-solving
    \end{itemize}
    \end{itemize}
    

\section{Internship Activities}
In the course of the internship, the Intern will primarily work on various projects. The following list contains example projects the intern will work on.

\begin{enumerate}
    \item GD NRW
    \begin{itemize}
        \item Digital asset management System (DAM) with an Geo-Metadatasystem
    \end{itemize}
    \item Open Pioneer
    \begin{itemize}
        \item Realization of a Digital Twin with Cesium and OpenLayers for NRW 
    \end{itemize}
    \end{enumerate}

\section{Internship Evaluation}
The Evaluation of the internship will be done in form of a report. The report will be written in English and will be submitted to the internship supervisor and to the university. The report wil be presented by the intern in a Wrap up Seminar. The report will contain a description of the internship activities and the learning objectives. The report will also contain a self evaluation of the intern. 

\section{Agreement}

We, the undersigned, agree to the terms of this Internship Learning Agreement and commit to support the intern to achieve the outlined learning objectives:
\\[48pt]
\noindent
\begin{tabular}{@{}p{2.5in}p{2.5in}@{}}
  \dotfill & \dotfill \\
  Intern's Signature & Date \\[5\bigskipamount]
  \dotfill & \dotfill \\
  Internship Supervisor & Date \\[5\bigskipamount]
  \dotfill & \dotfill \\
  con terra & Date \\[5\bigskipamount]
  \dotfill & \dotfill \\
  Academic Advisor's/University's Signature & Date \\[5\bigskipamount]


\end{tabular}

\end{document}
